\LARGE \bf Towards a Data-driven Approach to Motion Planning

### 2015-02-26 paper2015asml.tex
made some changes

% The following packages can be found on http:\\www.ctan.org
%\usepackage{graphics} % for pdf, bitmapped graphics files
%\usepackage{epsfig} % for postscript graphics files
%\usepackage{mathptmx} % assumes new font selection scheme installed
%\usepackage{times} % assumes new font selection scheme installed
%\usepackage{amsmath} % assumes amsmath package installed
%\usepackage{amssymb}  % assumes amsmath package installed
\usepackage{wrapfig}
\usepackage{graphicx,color}
\usepackage{adjustbox}

@@

%EDITING COMMANDS
\newcommand{\hilight}[1]{\colorbox{red}{#1}}
\newcommand{\todo}{\colorbox{red}{TODO}}
\newcommand{\tj}[1]{\ensuremath{\xi_\text{#1}}}

@@

Recent work has also addressed the task of making motions predictable (similar motions in similar environments and tasks) and/or legible (make it easier for human observers to understand the intent of the robot)~\cite{Beetz:2010}. Legibility makes it possible for human observers to understand clearly what a robot is intending to do, allowing them to modify their actions and motions if necessary. Predictability implies that the robot will always be consistent in its actions, removing the element of surprise for human observers. These concepts have been well-studies recently with the intent of measuring legibility~\cite{Lichtenthaler:2011}, using expressions to improve the readability of robots~\cite{Takayama:2011} and generating anticipation~\cite{Gielniak:2011}. In~\cite{Dragan:2013}, the notion of legibility was incorporated into a constrained trajectory optimization motion planner to generate motions that are more legible to human observers.

@@

We identified and computed multiple types of trajectory features. The first set of features we compute for each trajectory take into account the environment around the robot, the shape of the trajectory and the dynamics of the trajectory. These make up our unary features computed only on the input trajectory. We also include features that compare each trajectory to a nominal trajectory - these feature serve to characterize how much the trajectory deviates from the ``expected'' path. We go over these comparative features in the next section. First, we detail the features we computed on each trajectory \tj{} with waypoints $q_i$ where $i={0,\mathellipsis,n}$ and $n=|\tj{}|$. Note that our features are generic, i.e. they can be computed in the same manner for any robot arm trajectory. We believe that our methods should be easily extensible to robots other than the PR2 as well and individual trajectory classifiers could be built for each different robot arm in a similar manner.

@@

\subsection{Comparative Trajectory Features}
\label{subsec:multi_traj_feat}
We also wanted to design features that captured the difference between the planned trajectory and an expected path for the end-effector in the environment. The expected or nominal end-effector trajectories were created using a breadth-first search in a 3D voxel approximation of the planning problem. The environment model was first discretized into a voxel-grid, and voxels are marked as occupied or empty. Any voxel that is partially occupied is considered to be occupied. A 26-connected grid was used in the planning process to find a path in the voxel grid for a cubical shape moving from the start position of the end-effector of the arm to the desired goal position.  Essentially, this would be the optimal path followed by the end-effector from start to goal if it were modeled as a free-standing cube. Next, we compute comparison features between $\xi_{\text{BFS}}$ and three workspace trajectories for the elbow ($\xi_\text{elbow}$), wrist ($\xi_\text{wrist}$) and finger-tip ($\xi_\text{tip}$) links. The comparison features computed between each pair of trajectories are the Hausdorff distances~\cite{dubuisson1994modified} and Dynamic Time Warping~\cite{senin2008dynamic} distances.

@@

The dataset we have collected and the analysis we have already done in this paper will serve as a
 platform for further development of the idea of using 
a data-driven approach to motion planning. We intend to attempt to learn a cost function for describing the relation between the features and 
the ratings of the generated trajectories using inverse reinforcement learning. We hope to examine whether a cost function derived in this manner will 
lead to generation of more preferred trajectories. We would also like to extend our set of features to include more dynamic features to capture the effect 
that the dynamics of the motions have on the perception of the motion. The infrastructure that we have developed for generating and conducting 
surveys is fairly generic and could easily be extended to surveying people using trajectories from real robots. This is another avenue we intend to explore 
in the near future. We also intend to explore the potential for open-sourcing the data and infrastructure to allow other researchers to conduct surveys of their own.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section*{ACKNOWLEDGMENT}
We would like to thank Leila Takayama for valuable advice on structuring the online survey. We would like to thank Lydia Kavraki and Mark Moll for valuable discussions and suggestions. 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\bibliography{IEEEabrv,max,arjun}
\bibliographystyle{IEEEtran}

>>>>

% The following packages can be found on http:\\www.ctan.org
%\usepackage{graphics} % for pdf, bitmapped graphics files
%\usepackage{epsfig} % for postscript graphics files
%\usepackage{mathptmx} % assumes new font selection scheme installed
%\usepackage{times} % assumes new font selection scheme installed
%\usepackage{amsmath} % assumes amsmath package installed
%\usepackage{amssymb}  % assumes amsmath package installed
\usepackage{wrapfig}
\usepackage{graphicx,color,soul}
\usepackage{adjustbox}

@@

%EDITING COMMANDS
\newcommand{\hilight}[1]{\colorbox{yellow}{#1}}
\newcommand{\todo}{\colorbox{red}{TODO}}
\newcommand{\tj}[1]{\ensuremath{\xi_\text{#1}}}

@@

Recent work has also addressed the task of making motions predictable (similar motions in similar environments and tasks) and/or legible (make it easier for human observers to understand the intent of the robot)~\cite{Beetz:2010}. Legibility makes it possible for human observers to understand clearly what a robot is intending to do, allowing them to modify their actions and motions if necessary. Predictability implies that the robot will always be consistent in its actions, removing the element of surprise for human observers. These concepts have been well-studies recently with the intent of measuring legibility~\cite{Lichtenthaler:2011}, using expressions to improve the readability of robots~\cite{Takayama:2011} and generating anticipation~\cite{Gielniak:2011}. In~\cite{Dragan:2013}, the notion of legibility was incorporated into a constrained trajectory optimization motion planner to generate motions that are more legible to human observers,\hl{ while in}~\cite{mainprice2011planning} \hl{a cost-map was developed in conjunction with sampling based planning to produce trajectories in cluttered ienvironements.}

@@

We identified and computed multiple types of trajectory features. This set of features were selected to characterize the trajectories that were produced for the purpose of identifying the most informative sub-set. Developing a larger variety of more complicated and descriptive features is left as an avenue for future work.

The first set of features we compute for each trajectory take into account the environment around the robot, the shape of the trajectory and the dynamics of the trajectory. These make up our unary features computed only on the input trajectory. We also include features that compare each trajectory to a nominal trajectory - these feature serve to characterize how much the trajectory deviates from the ``expected'' path. We go over these comparative features in the next section. First, we detail the features we computed on each trajectory \tj{} with waypoints $q_i$ where $i={0,\mathellipsis,n}$ and $n=|\tj{}|$. Note that our features are generic, i.e. they can be computed in the same manner for any robot arm trajectory. We believe that our methods should be easily extensible to robots other than the PR2 as well and individual trajectory classifiers could be built for each different robot arm in a similar manner.

@@

\subsection{Comparative Trajectory Features}
\label{subsec:multi_traj_feat}
We also wanted to design features that captured the difference between the planned trajectory and an expected path for the end-effector in the environment.

{\bf Nominal Trajectory Generation}: \hl{The expected or nominal end-effector trajectories were created using a breadth-first search in a 3D grid approximation of the planning problem. We plan the path of the end-effector as if it were a }\emph{free-standing cube} \hl{that is not contrained by the kinematics of the arm to which it is attached. The environment model was first discretized into a voxel-grid, and voxels are marked as occupied or empty. Any voxel that is partially occupied is considered to be occupied.

The breadth-first search was conducted using this 26-connected grid to find a path in the voxel grid from the start position of the end-effector of the arm (the }\emph{xyz} \hl{coordinates from forward kinematics) to the desired goal position. By ignoring orientation and using BFS, we get a piece-wise collection of straight-line paths in the }{\bf workspace} \hl{from that start to goal points.}

Next, we compute comparison features between $\xi_{\text{BFS}}$ and three workspace trajectories for the elbow ($\xi_\text{elbow}$), wrist ($\xi_\text{wrist}$) and finger-tip ($\xi_\text{tip}$) links. The comparison features computed between each pair of trajectories are the Hausdorff distances~\cite{dubuisson1994modified} and Dynamic Time Warping~\cite{senin2008dynamic} distances. \hl{These features are used because of their applicability for comparing trajectories from location based services}~\cite{chen2013dynamic}.

@@

The dataset we have collected and the analysis we have already done in this paper will serve as a
 platform for further development of the idea of using 
a data-driven approach to motion planning. We intend to attempt to learn a cost function for describing the relation between the features and 
the ratings of the generated trajectories using inverse reinforcement learning. We hope to examine whether a cost function derived in this manner will 
lead to generation of more preferred trajectories. We would also like to extend our set of features to include more dynamic features to capture the effect 
that the dynamics of the motions have on the perception of the motion. \hl{Moreover, the feature set we describe in the paper should grow to further describe the spatial motions even more.} The infrastructure that we have developed for generating and conducting 
surveys is fairly generic and could easily be extended to surveying people using trajectories from real robots. This is another avenue we intend to explore 
in the near future. We also intend to explore the potential for open-sourcing the data and infrastructure to allow other researchers to conduct surveys of their own.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section*{ACKNOWLEDGMENT}
We would like to thank Leila Takayama for valuable advice on structuring the online survey. We would like to thank Lydia Kavraki,  Mark Moll, and Mike Phillips for valuable discussions and suggestions. 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\bibliography{IEEEabrv,max,arjun}
\bibliographystyle{IEEEtran}
